Project-I by Group CITYNAME

### 2015-11-01 report/paper.tex
Changed report tex file

\section{Summary}

>>>>

\section{Summary}
We analyzed a regression and classification datasets and that ridge regression and penalized logistic regression are reasonable fit.
We tried some feature transformation and found that polynomial feature transformation gives us a little improvement in final test error result. 
We estimate that the average test error for regression problem is $0.115\pm0.001$ on the test set, that is approximately one tenth of the variance of the output variable. The test error for classification problem is $0.167\pm0.001$.
